Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-05-02 paper/Analisis.tex
+ text for Nscatt section

In order to understand the morphology of the line we make a histogram of $<N_{scatt}>$  in function of $X_{m}$

as we think Nscatt is related with the double peacked line and maxima positions.

>>>>

In order to understand the morphology of the line we make histograms of $<N_{scatt}>$  in function of $X_{m}$ for both central Fig. ~\ref{fig:NscattHisto} and homogeneous distribution Fig. ~\ref{fig:NscattHistoHOM}. For the central distribution we found that for some value (put the value) of $N_{scatt}$ there is a predominant shift $X_{m}$. (Make position analysis of this photons). For te homogenepus distribution we found that most of the photons escape with just one scattering as a consequence that there are more photons near the surface and that rotating helps photons to escape easier. (improve this arguments with initial position analysis.)
